---
title: 'Grad Project: Week 12'
author: "Brian Detweiler"
date: "April 1, 2018"
output: html_document
---

```{r setup, include=FALSE, cache=TRUE}
# setwd('/home/bdetweiler/src/Data_Science/stat-8960-capstone-project')

library('knitr')
library("devtools")
library('MonetDB.R')
library('MonetDBLite')
library('MASS')
library('dbplyr')
library('DBI')
library('ggplot2')
library('scales')
library('ggjoy')
library('ggridges')
library('zoo')
library('TSA')
library('forecast')
library('reshape2')
library('modeest')
library('survey')
library('tidyverse')
library('boot')
library('broom')
library('beepr')
library('Deducer')
library('pROC')
library('dplyr')

set.seed(098114100)

knitr::opts_chunk$set(echo=TRUE, fig.height=5, fig.width=5, fig.align='center', scipen=1, digits=2)
options(max.print=1000000, tibble.print_max = Inf)
#MonetDBLite::monetdblite_shutdown()
con <- DBI::dbConnect(MonetDBLite::MonetDBLite(), "/home/bdetweiler/src/Data_Science/stat-8960-capstone-project/data/nrd_db")
hosp <- DBI::dbGetQuery(con, "SELECT * FROM nrd_hospital")

hosp$hosp_bedsize <- as.integer(hosp$hosp_bedsize)

hosp$h_contrl <- as.integer(hosp$h_contrl)
hosp$hosp_urcat4 <- as.integer(hosp$hosp_urcat4)
hosp$n_disc_u <- as.integer(hosp$n_disc_u)
hosp$n_hosp_u <- as.integer(hosp$n_hosp_u)
hosp$s_disc_u <- as.integer(hosp$s_disc_u)
hosp$s_hosp_u <- as.integer(hosp$s_hosp_u)
hosp$total_disc <- as.integer(hosp$total_disc)

hosp <- hosp %>%
  # Hospital control isn't quantifiable, it's categorical
  mutate(hosp_hcontrl_govt=as.integer(h_contrl == 1)) %>%
  mutate(hosp_hcontrl_priv_np=as.integer(h_contrl == 2)) %>%
  mutate(hosp_hcontrl_priv=as.integer(h_contrl == 3)) %>%
  # Swap the values of urban/rural categorization so that larger numbers == larger areas
  mutate(hosp_urcat4=replace(hosp_urcat4, hosp_urcat4==4, 0)) %>%
  mutate(hosp_urcat4=replace(hosp_urcat4, hosp_urcat4==3, 4)) %>%
  mutate(hosp_urcat4=replace(hosp_urcat4, hosp_urcat4==1, 3)) %>%
  mutate(hosp_urcat4=replace(hosp_urcat4, hosp_urcat4==4, 1)) %>%
  # Teaching isn't quantifiable, it's categorical
  mutate(hosp_ur_teach_metro=as.integer(hosp_ur_teach == 0)) %>%
  mutate(hosp_ur_teach_metro_teaching=as.integer(hosp_ur_teach == 1)) %>%
  mutate(hosp_ur_teach_non_metro=as.integer(hosp_ur_teach == 2)) 


 sample0 <- function(x, ...) x[sample.int(length(x), ...)]
 my.cost <- function(y, yhat) {
   return(mean((y - yhat) ^ 2))
 }
 cv.glm1 <- function(data, glmfit, cost, K=n, threshold) {

    # cross-validation estimate of error for glm prediction with K groups.
    # cost is a function of two arguments: the observed values and the
    # the predicted values.
  
    call <- match.call()
    if (!exists(".Random.seed", envir=.GlobalEnv, inherits = FALSE)) {
      runif(1)
    }
    seed <- get(".Random.seed", envir=.GlobalEnv, inherits = FALSE)
    n <- nrow(data)
    if ((K > n) || (K <= 1)) {
        stop("'K' outside allowable range")
    }
    K.o <- K
    K <- round(K)
    kvals <- unique(round(n / (1L:floor(n/2))))
    
    temp <- abs(kvals - K)
  
    if (!any(temp == 0)) {
        K <- kvals[temp == min(temp)][1L]
    }
   
    if (K != K.o) {
      warning(gettextf("'K' has been set to %f", K), domain = NA)
    }
    
    f <- ceiling(n / K)
    s <- sample0(rep(1L:K, f), n)

    n.s <- table(s)

#    glm.f <- formula(glmfit)
    glm.y <- glmfit$y
    
    cost.0 <- cost(glm.y, fitted(glmfit))
    
    ms <- max(s)
    
    CV <- 0
    Call <- glmfit$call
    
    i <- 1
    for(i in seq_len(ms)) {
        j.out <- seq_len(n)[(s == i)]
        j.in <- seq_len(n)[(s != i)]
        ## we want data from here but formula from the parent.
        Call$data <- data[j.in, , drop=FALSE]
        d.glm <- eval.parent(Call)
        d.glm
        p.alpha <- n.s[i]/n

        p.i <- as.vector(unlist(predict(d.glm, data[j.out, , drop=FALSE], type = "response"))) >= threshold
        cost.i <- cost(glm.y[j.out], p.i)
        cost.i
        CV <- CV + p.alpha * cost.i
        p <- as.vector(unlist(predict(d.glm, data, type = "response"))) >= threshold
        cost.0 <- cost.0 - p.alpha * cost(glm.y, p)
    }
    list(call = call, K = K,
         delta = as.numeric(c(CV, CV + cost.0)),  # drop any names
         seed = seed)
}


```

# At a glance

 * No longer looking for FMTs
 * Evaluating other variables of interest and looking for strong predictors, notably renal failure comorbidities
 * Began model fitting and evaluation

# Contingency plan

Having been unable to find FMTs in the NRD dataset, we need to take a different route.
If we can't look at FMTs for effect on readmissions, what *can* we look at?

We have a rich dataset of C. *diff* index admissions within the NRD dataset, and whether they were readmitted within
$d$ days. The index admission comes with a primary diagnosis and and up to 29 secondary diagnoses. 
However, they do not come with  a *present on admission* indicator, so we cannot tell directly what ICD-9-CM codes were added on 
admission and what codes were acquired during their hospital stay. The NRD does however, provide us
with a list of 29 comorbidity indicators:

|     | Column             | Description                                                                           |
|-----|--------------------|---------------------------------------------------------------------------------------|
| 1   | CM_AIDS            | Acquired immune deficiency syndrome                                                   |
| 2   | CM_ALCOHOL         | Alcohol abuse                                                                         |
| 3   | CM_ANEMDEF         | Deficiency anemias                                                                    |
| 4   | CM_ARTH            | Rheumatoid arthritis/collagen vascular diseases                                       | 
| 5   | CM_BLDLOSS         | Chronic blood loss anemia                                                             |
| 6   | CM_CHF             | Congestive heart failure                                                              |
| 7   | CM_CHRNLUNG        | Chronic pulmonary disease                                                             |
| 8   | CM_COAG            | Coagulopath                                                                           |
| 9   | CM_DEPRESS         | Depression                                                                            |
| 10  | CM_DM              | Diabetes, uncomplicated                                                               |
| 11  | CM_DMCX            | Diabetes with chronic complications                                                   |
| 12  | CM_DRUG            | Drug abuse                                                                            |
| 13  | CM_HTN_C           | Hypertension, uncomplicated and complicated                                           |
| 14  | CM_HYPOTHY         | Hypothyroidism                                                                        |
| 15  | CM_LIVER           | Liver disease                                                                         |
| 16  | CM_LYMPH           | Lymphoma                                                                              |
| 17  | CM_LYTES           | Fluid and electrolyte disorders                                                       |
| 18  | CM_METS            | Metastatic cancer                                                                     |
| 19  | CM_NEURO           | Other neurological disorders                                                          |
| 20  | CM_OBESE           | Obesity                                                                               |
| 21  | CM_PARA            | Paralysis                                                                             |
| 22  | CM_PERIVASC        | Peripheral vascular disorders                                                         |
| 23  | CM_PSYCH           | Psychoses                                                                             |
| 24  | CM_PULMCIRC        | Pulmonary circulation disorders                                                       |
| 25  | CM_RENLFAIL        | Renal failure                                                                         |
| 26  | CM_TUMOR           | Solid tumor without metastasis                                                        |
| 27  | CM_ULCER           | Peptic ulcer disease excluding bleeding                                               |
| 28  | CM_VALVE           | Valvular disease                                                                      |
| 29  | CM_WGHTLOSS        | Weight loss                                                                           |

We can examine which among these indicators, as well as other factors, have a higher effect on readmissions.

```{r, echo=FALSE, cache=TRUE, message=FALSE, warning=FALSE}
readm.90 <- read_csv('/home/bdetweiler/src/Data_Science/stat-8960-capstone-project/data/cdiff-readmissions-90-day-window.csv')

readm.90 <- merge(readm.90, hosp, by.x=c("cluster", "nrd_year"), by.y=c("hosp_nrd", "nrd_year"))

readm.90 <- readm.90 %>%
  # Hospital control isn't quantifiable, it's categorical
  mutate(pay_NA=as.integer(pay1 < 0)) %>%
  mutate(pay_other=as.integer(pay1 == 6)) %>%
  mutate(pay_nc=as.integer(pay1 == 5)) %>%
  mutate(pay_self=as.integer(pay1 == 4)) %>%
  mutate(pay_priv_ins=as.integer(pay1 == 3)) %>%
  mutate(pay_medicaid=as.integer(pay1 == 2)) %>%
  mutate(pay_medicare=as.integer(pay1 == 1))

```

## Checking for independence

Most of the variables are categorical. Before we build a model, we need to assess independent variables for multicollinearity.
We can use $\chi$-square tests for independence coupled with Cramer's Contingency Coefficient, also known as Cramer's phi ($\phi_c$) or
[Cramer's V](https://en.wikipedia.org/wiki/Cram%C3%A9r%27s_V).

```{r, echo=FALSE, cache=TRUE, message=FALSE, warning=FALSE}
columns.to.test <- c("female", 
                     "aweekend", 
                     "cm_aids", 
                     "cm_alcohol", 
                     "cm_anemdef", 
                     "cm_art", 
                     "cm_bldloss", 
                     "cm_chf", 
                     "cm_chrnlung", 
                     "cm_coag", 
                     "cm_depress", 
                     "cm_dm", 
                     "cm_dmcx", 
                     "cm_drug", 
                     "cm_htn_c", 
                     "cm_hypothy", 
                     "cm_liver", 
                     "cm_lymph", 
                     "cm_lytes", 
                     "cm_mets", 
                     "cm_neur", 
                     "cm_obese", 
                     "cm_para", 
                     "cm_perivasc", 
                     "cm_psych", 
                     "cm_pulmcirc", 
                     "cm_renlfail", 
                     "cm_tumor", 
                     "cm_ulcer", 
                     "cm_valve", 
                     "cm_wghtloss", 
                     "hosp_bedsize", 
                     "hosp_hcontrl_govt", 
                     "hosp_hcontrl_priv_np", 
                     "hosp_ur_teach_metro", 
                     "hosp_ur_teach_metro_teaching", 
                     "pay_other", 
                     "pay_nc", 
                     "pay_self", 
                     "pay_priv_ins", 
                     "pay_medicaid", 
                     "pay_medicare") 

correlated <- data.frame(col1=c(NA), col2=c(NA), pval=c(NA), v=c(NA))
count <- 1

for (i in 1:(length(columns.to.test) - 1)) {
  for (j in (i + 1):length(columns.to.test)) {
    
    count <- count + 1
    
    readmitted.1 <- readm.90 %>% 
      dplyr::filter(readmitted == 1) %>% 
      dplyr::select(dplyr::matches(columns.to.test[i])) %>%
      sum() %>%
      as.numeric()

    readmitted.0 <- abs(readmitted.1 - 
                          (readm.90 %>% 
                             dplyr::filter(readmitted == 1) %>% 
                             dplyr::summarise(n()))) %>%
      as.numeric()
    
    non.readmitted.1 <- readm.90 %>% 
      dplyr::filter(readmitted == 0) %>% 
      dplyr::select(dplyr::matches(columns.to.test[j])) %>%
      sum() %>%
      as.numeric()
    
    non.readmitted.0 <- abs(readmitted.1 - 
                              (readm.90 %>% 
                                dplyr::filter(readmitted == 0) %>% 
                                dplyr::summarise(n()))) %>%
      as.numeric()
      
    
    tbl <- matrix(data=c(readmitted.0, readmitted.1, non.readmitted.0, non.readmitted.1), nrow=2, ncol=2, byrow=T)
    
    dimnames(tbl) <- list(Readmission=c('Readm', 'Non-Readm'), Variable=c(columns.to.test[i], columns.to.test[j]))

    chi2 <- chisq.test(tbl, correct=F)
     
    # Cramer's V
    v <- sqrt(chi2$statistic / sum(tbl))
    
    correlated <- bind_rows(correlated, data.frame(col1=columns.to.test[i], col2=columns.to.test[j], pval=chi2$p.value, v=v[[1]]))
  }
}

correlated$pval <- as.numeric(correlated$pval)
correlated$v <- as.numeric(correlated$v)

final.correlated <- correlated %>% 
  dplyr::arrange(desc(v)) %>%
  dplyr::filter(v > 0.7) %>%
  dplyr::filter(!is.na(v)) %>%
  dplyr::select(-pval)
  
```

Selecting only those with a v of 0.70 or greater, we find

```{r, echo=FALSE, cache=TRUE}
kable(final.correlated, format = "markdown", col.names = c("Column A", "Column B", "Cramer's V"))
```


Pay type seems to correlate strongly with the hospital urban/rural and teaching indicators. We are interested in the hospital
types more than the pay types, so we'll remove the pay types from the model. 

That leaves us with a few comorbidities and the female indicator being correlated.

```{r, echo=FALSE, cache=TRUE}
final.correlated.reduced <- final.correlated %>% 
  filter(!grepl("pay", col1, fixed = TRUE)) %>%
  filter(!grepl("pay", col2, fixed = TRUE)) 
kable(final.correlated.reduced, format = "markdown", col.names = c("Column A", "Column B", "Cramer's V"))

aids <- (readm.90 %>% filter(cm_aids == 1)) %>% nrow() / nrow(readm.90) * 100
htn <- (readm.90 %>% filter(cm_htn_c == 1)) %>% nrow() / nrow(readm.90) * 100
lytes <- (readm.90 %>% filter(cm_lytes == 1)) %>% nrow() / nrow(readm.90) * 100
lymph <- (readm.90 %>% filter(cm_lymph == 1)) %>% nrow() / nrow(readm.90) * 100
ulcer <- (readm.90 %>% filter(cm_ulcer == 1)) %>% nrow() / nrow(readm.90) * 100
renal <- (readm.90 %>% filter(cm_renlfail == 1)) %>% nrow() / nrow(readm.90) * 100

```

If we dig into this a bit, we find that **cm_aids** accounts for `r aids`% of the dataset, 
**cm_lymph** accounts for `r lymph`%, and **ulcer** accounts for `r ulcer`%, so any correlation
should be minimally impactful, and we will probably end up removing them from the model altogether, 
along with the pay types.

Now, we'll run the full with all variables of interest for each year and print out the fitting times
below.

```{r, echo=FALSE, cache=TRUE}

models.by.year <- list()

years <- c(2010, 2011, 2012, 2013, 2014)
y <- 2010
sw.total <- Sys.time()
for (y in years) {

  readm.by.year <- readm.90 %>% 
    filter(nrd_year == y)
  
  print(paste0("Year: ", y))
  
  cdiff.design <- svydesign(ids = ~cluster, 
                            data = readm.by.year, 
                            weights = ~weight, 
                            strata = ~stratum)
  sw.start <- Sys.time()
  m <- svyglm(readmitted~age.start +
                         hosp_hcontrl_govt +
                         hosp_hcontrl_priv_np +
                         hosp_urcat4 +
                         hosp_ur_teach_metro +
                         hosp_ur_teach_metro_teaching +
                         hosp_bedsize +
                         female +
                         cm_aids +
                         cm_alcohol +
                         cm_anemdef +
                         cm_arth +
                         cm_bldloss +
                         cm_chf +
                         cm_chrnlung +
                         cm_coag +
                         cm_depress +
                         cm_dm +
                         cm_dmcx +
                         cm_drug +
                         cm_htn_c +
                         cm_hypothy +
                         cm_liver +
                         cm_lymph +
                         cm_lytes +
                         cm_mets +
                         cm_neuro +
                         cm_obese +
                         cm_para +
                         cm_perivasc +
                         cm_psych +
                         cm_pulmcirc +
                         cm_renlfail +
                         cm_tumor +
                         cm_ulcer +
                         cm_valve +
                         cm_wghtloss,
              design=as.svrepdesign(cdiff.design), 
              family=quasibinomial, 
              return.replicates=TRUE)
  sw.end <- Sys.time()
  print(sw.end - sw.start)
  beep(3) 
  summary(m)
  models.by.year[[y]] <- m
}
print(Sys.time() - sw.total)
# Expect 20 minutes
```

```{r, echo=FALSE, cache=TRUE}
coef.2010 <- tidy(summary(models.by.year[[2010]])$coefficients) %>% 
  filter(.rownames != "(Intercept)") %>%
  arrange(desc(Pr...t..))

coef.2011 <- tidy(summary(models.by.year[[2011]])$coefficients) %>% 
  filter(.rownames != "(Intercept)") %>%
  arrange(desc(Pr...t..))

coef.2012 <- tidy(summary(models.by.year[[2012]])$coefficients) %>% 
  filter(.rownames != "(Intercept)") %>%
  arrange(desc(Pr...t..))

coef.2013 <- tidy(summary(models.by.year[[2013]])$coefficients) %>% 
  filter(.rownames != "(Intercept)") %>%
  arrange(desc(Pr...t..))

coef.2014 <- tidy(summary(models.by.year[[2014]])$coefficients) %>% 
  filter(.rownames != "(Intercept)") %>%
  arrange(desc(Pr...t..))

coef.2010$year <- 2010
coef.2011$year <- 2011
coef.2012$year <- 2012
coef.2013$year <- 2013
coef.2014$year <- 2014

coefs <- bind_rows(coef.2010, coef.2011, coef.2012, coef.2013, coef.2014)

coef.names <- coefs %>% 
  dplyr::select(.rownames) %>% 
  unique() %>% 
  pull(.rownames)

#length(coef.names)
name <- coef.names[27]
```

Now, we'll plot each coefficient by year, showing it's effect with confidence interval and labeled with $p$-values, showing
whether they were significant (<0.05) or not. 

```{r coefficients, echo=FALSE, cache=TRUE, fig.height=5, fig.width=6, fig.align="center"}
for (name in coef.names) {
  coefs <- mutate(coefs, Pr...t..=round(Pr...t.., 6))
  this.coef <- coefs %>% filter(.rownames == name)
  this.coef <- this.coef %>% 
    mutate(significant=ifelse(Pr...t.. < 0.05, 1, 0))

  p <- this.coef %>%
    ggplot(aes(year, Estimate, label = Pr...t..)) +
      geom_bar(stat="identity") +
      geom_errorbar(aes(ymin = (Estimate - Std..Error), ymax = (Estimate + Std..Error)), width = 0.2) +
      geom_label(aes(fill=factor(round(significant, 6))), colour="white", vjust=1.4, fontface = "bold") +
      labs(title=paste0("Coefficient estimate for ", name), x="Year", y="Coef. est.", fill="Significant")
  
  print(p)

}

#(readm.90 %>% filter(cm_renlfail == 1) %>% dplyr::select(readmitted) %>% sum()) / readm.90 %>% filter(cm_renlfail == 1) %>% nrow()
```


At this point, we must do some model selection. We will strive for parsimony while still trying to explain as much
of the variance as possible. To do this, we will remove the least significant variable and refit the model. We do this
iteratively (step-wise) until there are only significant coefficients left.

This will be the goal for next week.

```{r, echo=FALSE, cache=TRUE}
#count.df <- data.frame(year.2010.count=c(NA), 
                       #year.2011.count=c(NA),
                       #year.2012.count=c(NA),
                       #year.2013.count=c(NA),
                       #year.2014.count=c(NA))
#train.count.by.year <- c()
#test.count.by.year <- c()
#
#years <- c(2010, 2011, 2012, 2013, 2014)
#y <- 2010
#for (y in years) {

  #readm.by.year <- readm.90 %>% 
    #filter(nrd_year == y)
  #
  #print(paste0("Year: ", y))
  #
  #cdiff.design <- svydesign(ids = ~cluster, 
                            #data = readm.90, 
                            #weights = ~weight, 
                            #strata = ~stratum)
  #sw.start <- Sys.time()
  #m <- svyglm(readmitted~age.start +
                         #hosp_hcontrl_govt +
                         #hosp_hcontrl_priv_np +
                         #hosp_urcat4 +
                         #hosp_ur_teach_metro +
                         #hosp_ur_teach_metro_teaching +
                         #hosp_bedsize +
                         #female +
                         #cm_aids +
                         #cm_alcohol +
                         #cm_anemdef +
                         #cm_arth +
                         #cm_bldloss +
                         #cm_chf +
                         #cm_chrnlung +
                         #cm_coag +
                         #cm_depress +
                         #cm_dm +
                         #cm_dmcx +
                         #cm_drug +
                         #cm_htn_c +
                         #cm_hypothy +
                         #cm_liver +
                         #cm_lymph +
                         #cm_lytes +
                         #cm_mets +
                         #cm_neuro +
                         #cm_obese +
                         #cm_para +
                         #cm_perivasc +
                         #cm_psych +
                         #cm_pulmcirc +
                         #cm_renlfail +
                         #cm_tumor +
                         #cm_ulcer +
                         #cm_valve +
                         #cm_wghtloss,
              #design=as.svrepdesign(cdiff.design), 
              #family=quasibinomial, 
              #return.replicates=TRUE)
  #sw.end <- Sys.time()
  #print(sw.end - sw.start)
  #beep(3) 
  #summary(m)
#(readm.90 %>% filter(cm_renlfail == 1) %>% dplyr::select(readmitted) %>% sum()) / readm.90 %>% filter(cm_renlfail == 1) %>% nrow()
  ##readm.90$age.0.5 <- as.integer(readm.90$age.start > 0 & readm.90$age.start <= 5)
  ##readm.90$age.5.10 <- as.integer(readm.90$age.start > 5 & readm.90$age.start <= 10)
  ##readm.90$age.10.15 <- as.integer(readm.90$age.start > 10 & readm.90$age.start <= 15)
  ##readm.90$age.15.20 <- as.integer(readm.90$age.start > 15 & readm.90$age.start <= 20)
  ##readm.90$age.20.25 <- as.integer(readm.90$age.start > 20 & readm.90$age.start <= 25)
  ##readm.90$age.25.30 <- as.integer(readm.90$age.start > 25 & readm.90$age.start <= 30)
  ##readm.90$age.30.35 <- as.integer(readm.90$age.start > 30 & readm.90$age.start <= 35)
  ##readm.90$age.35.40 <- as.integer(readm.90$age.start > 35 & readm.90$age.start <= 40)
  ##readm.90$age.40.45 <- as.integer(readm.90$age.start > 40 & readm.90$age.start <= 45)
  ##readm.90$age.45.50 <- as.integer(readm.90$age.start > 45 & readm.90$age.start <= 50)
  ##readm.90$age.50.55 <- as.integer(readm.90$age.start > 50 & readm.90$age.start <= 55)
  ##readm.90$age.55.60 <- as.integer(readm.90$age.start > 55 & readm.90$age.start <= 60)
  ##readm.90$age.60.65 <- as.integer(readm.90$age.start > 60 & readm.90$age.start <= 65)
  ##readm.90$age.65.70 <- as.integer(readm.90$age.start > 65 & readm.90$age.start <= 70)
  ##readm.90$age.70.75 <- as.integer(readm.90$age.start > 70 & readm.90$age.start <= 75)
  ##readm.90$age.75.80 <- as.integer(readm.90$age.start > 75 & readm.90$age.start <= 80)
  ##readm.90$age.80.85 <- as.integer(readm.90$age.start > 80 & readm.90$age.start <= 85)
  ##readm.90$age.85.90 <- as.integer(readm.90$age.start > 85 & readm.90$age.start <= 90)
  ##readm.90$age.90 <- as.integer(readm.90$age.start > 90)
  #
  ## dplyr::select(readm.90, starts_with("age")) %>% colSums()
#
  #unique(readm.by.year$readmitted)
  #unique(readm.by.year$age.start)
  #unique(readm.by.year$cm_renlfail)
  #
  ## K-fold Cross-Validation
  ## cv.error <- cv.glm(readm.by.year, m, K=10)
  #
  ##cv.error <- cv.glm1(readm.by.year, m, my.cost, K=3, threshold=0.05)
  ##cv.error.1 <- cv.glm1(readm.by.year, m, my.cost, K=3, threshold=0.5)
  ##cv.error.2 <- cv.glm1(readm.by.year, m, my.cost, K=3, threshold=0.75)
#
  ##cv.error$delta
  ##cv.error.1$delta
  ##cv.error.2$delta
  ##library('beepr')
  ##beep(3)
#
  #
  #readm.90 %>% 
    #ggplot(aes(age.start + cm_renlfail, readmitted)) +
      #geom_bin2d(bins = 30) +
      #geom_smooth(method = "glm", method.args = list(family = "binomial")) +
      ##geom_point(data = pred.df, aes(x=Age, y=Prob)) +
      #labs(title="Logistic Regression of Readmission by Age", x="Age at last admission", y="Readmitted (1 = Yes, 0 = No)")
  #
  #log.odds <- function(age, cm_renlfail) {
    #return(exp(coef(m)[[1]] + (coef(m)[[2]] * age)  + (coef(m)[[3]] * cm_renlfail)))
  #}
  #
  #ages <- rep(seq(1:90), 2)
  #cm_renlfail <- c(rep(0, 90), rep(1, 90))
  #logreg <- as.data.frame(cbind(ages, cm_renlfail, odds=log.odds(ages, cm_renlfail)))
  #
  #logreg$cm_renlfail <- factor(logreg$cm_renlfail)
  
  ##logreg %>%
    #ggplot(aes(ages, odds, group=cm_renlfail, col=cm_renlfail)) +
      #geom_line() +
      #geom_hline(yintercept = 0.5, col="red") +
      ##labs(title=paste0("Odds ratio of 90 day readmission given age and renal failure comorbidity, ", y), 
           #y="Odds Ratio", 
           #x="Age", 
           #col="Renal")
#}

#count.df <- rbind(count.df, count.by.year)
#count.df <- count.df[-1,]
```


# Next steps

Model selection, analysis, and interpretation.