---
title: 'Grad Project: Week 7'
author: "Brian Detweiler"
date: "February 25, 2018"
output: html_document
---

```{r setup, include=FALSE, cache=TRUE}
# setwd('/home/bdetweiler/src/Data_Science/stat-8960-capstone-project')

library("devtools")
library('MonetDB.R')
#install.packages('MonetDBLite')
library('MonetDBLite')
library('dplyr')
library('dbplyr')
library('DBI')
library('ggplot2')
library('scales')
library('ggjoy')
library('ggridges')
library('zoo')
library('TSA')
library('forecast')
library('reshape2')
library('modeest')

knitr::opts_chunk$set(echo=TRUE, fig.height=5, fig.width=5, fig.align='center', scipen=1, digits=2)
options(max.print=1000000, tibble.print_max = Inf)
#MonetDBLite::monetdblite_shutdown()
#con <- DBI::dbConnect(MonetDBLite::MonetDBLite(), "/home/bdetweiler/src/Data_Science/stat-8960-capstone-project/data/nrd_db")
```

```{r, echo=FALSE, cache=TRUE}
cdiff <- read.csv('/home/bdetweiler/src/Data_Science/stat-8960-capstone-project/data/cdiff-nrd.csv', stringsAsFactors = FALSE)
```

```{r, echo=FALSE, cache=TRUE}
rowcount <- count(cdiff)[[1]]
patients <- length(unique(cdiff$nrd_visitlink))
```

# At a glance

 * NRD data sets fully imported into MonetDB
 * Ran query for C. *diff* cases 
 * `r patients` patients tracked across `r rowcount` observations (`r rowcount - patients` readmissions)

# Never enough memory

Time really got away from me this past week! My day job had me occupied for most of the weekend
so I've been playing catch-up this week.

The NRD dataset has given me quite a bit more trouble than the NIS, mainly due to its massive file sizes,
but also due to the way they switched formats in the fourth quarter of 2015. That small change pretty much
doubled the complexity. The Q4 2015 columns couldn't be stored in the normal columns, so we needed to
create additional columns specifically for Q4 2015. This resulted in 338 columns. Keeping track of all those
while importing was a challenge.

Furthermore, unlike the NIS dataset, where I was able to read a year's worth of data into memory at a time on
my 64 GB machine, reading in the core file, the Dx Pr Groups file, and the Severity file, *and then* merging 
them proved to be too much as I watched it consume all of my memory and then eventually all of my swap. 

I decided to take another route, inspired by a recent project at my day job, which also involved sucking in
large amounts of data from CSV files and importing them into a database. Our solution to the large file problem
was to split the files into more readable chunks.

# Splitting the files

`split` is a core utility found on *nix operating systems that takes a file and splits it into multiple files
based on either bytes or lines. In order to write simple reusable \textsf{R} code, we'll arbitrarily pick
4 as a reasonable number of files. This will allow us to predictably loop over the import code import each file one at a time.

To start, let's get the line count of the core files, noting that the Dx Pr and Severity files have the same lengths.

```
$ wc -l NRD_2010_Core_V2.CSV | awk '{print $1"/4"}' | bc
3476902
```

Now we can split the files. the `-l` option tells split how many lines to use for each file, and the `-d` option 
tells it to use a decimal incrementor for each split file name, rather than the default alpha.

```
$ split -l3476902 -d NRD_2010_Core_V2.CSV NRD_2010_Core_split
$ split -l3476902 -d NRD_2010_DX_PR_GRPS_V2.CSV NRD_2010_DX_PR_GRPS_split_
$ split -l3476902 -d NRD_2010_Severity_V2.CSV NRD_2010_Severity_split_
$ l -h *split* | sed -e 's/  / /g' | cut -f5,9 -d$' '
1.3G NRD_2010_Core_split_00
1.3G NRD_2010_Core_split_01
1.3G NRD_2010_Core_split_02
1.3G NRD_2010_Core_split_03
745 NRD_2010_Core_split_04
867M NRD_2010_DX_PR_GRPS_split_00
865M NRD_2010_DX_PR_GRPS_split_01
866M NRD_2010_DX_PR_GRPS_split_02
866M NRD_2010_DX_PR_GRPS_split_03
539 NRD_2010_DX_PR_GRPS_split_04
282M NRD_2010_Severity_split_00
282M NRD_2010_Severity_split_01
282M NRD_2010_Severity_split_02
282M NRD_2010_Severity_split_03
170 NRD_2010_Severity_split_04
```
We see here even the splits for the core files are over a gig each. But the DX PR files with their expansive columns
eat memory alive when reading in as a data frame. With these splits though, we're able to get through the processing
with just enough memory.

# Data in data out

Once it's all loaded in the database, the first thing we want to do is query for all the C. *diff* cases like we did
with the NIS dataset and write those out to a CSV file for future use. As mentioned before, a `select *` query on
a column store database is very inefficient and not really now these databases are intended to be used.  
We'll want to write this out, because we don't want to have to do this query again.

This time, in addition to the ICD-9 code of **00845**, we also need to look for the ICD-10 code, **A04.7**. 
In addition to querying for C. *diff* cases, we need to get the **nrd_visit** link, and return every row
with that visitlink in it. Patients may be readmitted and contract C. *diff* on the readmission, or they 
may have initially been admitted with C. *diff* and later readmitted for something else. Whatever the case,
we want a complete picture of these patients' visits. 

```
con <- DBI::dbConnect(MonetDBLite::MonetDBLite(), "data/nis_db")

q <- DBI::dbGetQuery(con, "SELECT *
                             FROM nrd
                            WHERE nrd_visitlink in (SELECT nrd_visitlink
                                                      FROM nrd 
                                                     WHERE dx1      = '00845' OR 
                                                           dx2      = '00845' OR
                                                           dx3      = '00845' OR
                                                           dx4      = '00845' OR
                                                           dx5      = '00845' OR
                                                           dx6      = '00845' OR
                                                           dx7      = '00845' OR
                                                           dx8      = '00845' OR
                                                           dx9      = '00845' OR
                                                           dx10     = '00845' OR
                                                           dx11     = '00845' OR
                                                           dx12     = '00845' OR
                                                           dx13     = '00845' OR
                                                           dx14     = '00845' OR
                                                           dx15     = '00845' OR
                                                           dx16     = '00845' OR
                                                           dx17     = '00845' OR
                                                           dx18     = '00845' OR
                                                           dx19     = '00845' OR
                                                           dx20     = '00845' OR
                                                           dx21     = '00845' OR
                                                           dx22     = '00845' OR
                                                           dx23     = '00845' OR
                                                           dx24     = '00845' OR
                                                           dx25     = '00845' OR
                                                           dx26     = '00845' OR
                                                           dx27     = '00845' OR
                                                           dx28     = '00845' OR
                                                           dx29     = '00845' OR
                                                           dx30     = '00845' OR
                                                           i10_dx1  = 'A047'  OR
                                                           i10_dx2  = 'A047'  OR
                                                           i10_dx3  = 'A047'  OR
                                                           i10_dx4  = 'A047'  OR
                                                           i10_dx5  = 'A047'  OR
                                                           i10_dx6  = 'A047'  OR
                                                           i10_dx7  = 'A047'  OR
                                                           i10_dx8  = 'A047'  OR
                                                           i10_dx9  = 'A047'  OR
                                                           i10_dx10 = 'A047'  OR
                                                           i10_dx11 = 'A047'  OR
                                                           i10_dx12 = 'A047'  OR
                                                           i10_dx13 = 'A047'  OR
                                                           i10_dx14 = 'A047'  OR
                                                           i10_dx15 = 'A047'  OR
                                                           i10_dx16 = 'A047'  OR
                                                           i10_dx17 = 'A047'  OR
                                                           i10_dx18 = 'A047'  OR
                                                           i10_dx19 = 'A047'  OR
                                                           i10_dx20 = 'A047'  OR
                                                           i10_dx21 = 'A047'  OR
                                                           i10_dx22 = 'A047'  OR
                                                           i10_dx23 = 'A047'  OR
                                                           i10_dx24 = 'A047'  OR
                                                           i10_dx25 = 'A047'  OR
                                                           i10_dx26 = 'A047'  OR
                                                           i10_dx27 = 'A047'  OR
                                                           i10_dx28 = 'A047'  OR
                                                           i10_dx29 = 'A047'  OR
                                                           i10_dx30 = 'A047')")
write.csv(q, 'data/cdiff-nrd.csv', row.names=FALSE)

```

The resulting CSV is 1.4 GB, which is manageable.


Any kind of descriptive statistics on this set as-is is not very useful because these are not unique samples like the NIS dataset, but 
rather repeat patients tracked across visits, which breaks the independence assumption. 

We will need to be a little more sophisticated about our analysis. AHRQ leaves it up to the analyst (that's us!) to link the patients,
so we will need to devise a way to do that going forward.

But very quickly, we can see that there are `r rowcount` observations and `r patients` unique patients. 
That means that `r (rowcount - patients)` of the observations are repeat visits, on which we can track a patient's readmission.

# Next Steps

At this point I have everything I need to begin a thorough analysis. 

With just over a month and a half left before a final deliverable is due, I plan on spending most of March building and
testing models, and the first half of April writing up my findings for presentation.

